---
title: "Using the Tennis Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the Tennis Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Determining tennis match outcomes 
The main function of the "Tennis" package is to determine the outcome of a singles tennis match between two players given a hypothetical number of aces each player served in a match. First, load the package.

```{r setup}
library(tennis)
```

Then, call the `tennis_predict()` function and give the necessary parameters, Player 1's number of aces and Player 2's number of aces. 

```{r}
tennis_predict(player1_aces = 12, player2_aces = 34)
```

This returns a string that will tell you the predicted outcome of the match. 

## Tennis Data
There is also a built in data set that describes the match outcomes of 14 tennis matches from 2010-2023. 

```{r}
tennis::tennis
```

