---
title: "Using the Tennis Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the Tennis Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Determining tennis match outcomes 
What is an ace? It refers to when a player serves the ball and the receiving opponent does not make contact with the ball and is unable to return it. The main function of the "Tennis" package is to determine the outcome of a singles tennis match between two players given a hypothetical number of aces each player served in a match. First, load the package.

```{r setup}
library(tennis)
```

Then, call the `tennis_predict()` function and give the necessary parameters, Player 1's number of aces and Player 2's number of aces. 

```{r}
tennis_predict(player1_aces = 12, player2_aces = 34)
```

This returns a string that will tell you the predicted outcome of the match. 

## Predicting Tennis Match Outcomes Via Probability
The second model, `tennis_predict2`, is more fine-tuned and will provide the user with the probabilty of success for each player. It takes the same parameters as the `tennis_predict` function.

```{r}
tennis_predict2(12, 34)
```

This model has used the log odds to determine that player 1 has about a 57% probability of winning the match, and player 2 has about a 43% chance of winning based on their aces.

## Tennis Data
There is also a built in data set that describes the match outcomes of 14 tennis matches from 2010-2023. 

```{r}
tennis::tennis
```

Now, let's see how well our model works by comparing it to real outcomes from our dataset. In a 2019 match, Player 1 (Nadal) played Player 2 (Medvedev). Nadal scored 5 aces while Medvedev scored 14, let's see what our model has to say.

```{r}
tennis_predict(5, 14)
```

Our model says predicts that Medvedev will win this match. However, Nadal actually won this match. So this model is not 100% reliable.

The second predictive model says: 

```{r}
tennis_predict2(5, 14)
```

Nadal has a 53% chance of winning, and Medvedev has a 47% chance of winning. This is more accurate than the last model as it predicted correctly.
